---
title: "Practica-09-09-2020"
author: "ASA"
date: "2022-09-08"
output: html_document
---

```{r setup, include=FALSE}
#install.packages("knitr")
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```


En esta practica realizaremos algunas simulaciones sencillaz. 

Primero simulemos el modelo SIR (susceptible-Infected-Recovered).

```{r}

 # SIR model (Suceptible Infected Removed)
 # SIR(S0, I0, p)
   # S0 : Poblacion susceptible inicial, no infectada
   # I0 : Poblacion infectada inicial, infectada
   # p  : Probabilidad de que una persona sana sea infectada tras tener contacto con
   #      alguien infectado


SIR<- function(S0,I0,p){
  
  r1= list()
  X= list()
  Y= list()
  W= list()
  i=1
  while (S0>0){
    
    #Selecciona aleatoriamente los infectados
    C<- rbinom( S0, I0, p)
    print(C)
    #Cuenta el numero de infectados en la muestra aleatoria
    I1<-length(C[C>0]) 
    print(I1)
    
    #Actualiza datos
    S0<- S0-I1
    I0<- I0+I1
    
    X[i]<- S0
    Y[i]<- I0
    W[i]<- I1
    i=i+1
    
  }
  
  r1<- list()
  r1[[1]]<- X
  r1[[2]]<- Y
  r1[[3]]<- W
  
  return(r1)  
  
}

Z<-SIR(160,3,0.004)

X<- Z[[1]]
Y<- Z[[2]]
W<- Z[[3]]
X<- unlist(X)
Y<- unlist(Y)
W<- unlist(W)
#plot(X,cex=2)
#plot(Y)
plot(X, xlab="time (t).", ylab= "Susceptible number", 
     cex=1, type="o", xlim=c(0,30), ylim=c(0,100) , lty="solid",xaxp=c(0,30,10),yaxp=c(0,100,100))

plot(Y, xlab="time (t).", ylab= "Total Infected number", 
     cex=1, type="o", xlim=c(0,30), ylim=c(0,100) , lty="solid",xaxp=c(0,30,10),yaxp=c(0,100,100))



plot(W, xlab="time (t).", ylab= "Infected number", 
     cex=1, type="o", xlim=c(0,30), ylim=c(0,100) , lty="solid",xaxp=c(0,30,10),yaxp=c(0,100,100))



```

Ahora, simulamos el proceso de ruina de un jugador.

```{r pressure}
# gamblersruin.R
# Example 1.11

# gamble(k, n, p)
  #   k: Gambler's initial state
  #   n: Gambler plays until either $n or Ruin
  #   p: Probability of winning $1 at each play
  #   Function returns 1 if gambler is eventually ruined
  #                    returns 0 if gambler eventually wins $n
  
gamble <- function(k,limit,p, graficar) {
  
	stake <- k # Capital 
	n <- 0
	steps <- c(NULL)
	while (stake > 0 & stake < limit & n < 1000 ) {
	  
	  n <- n + 1
	  
		bet <- sample(c(-1,1),1,prob=c(1-p,p))
		stake <- stake + bet
		
		steps <- c(steps, bet)
		
	}
	
	#graficar las simulaciones
  
  if(graficar == TRUE) {
    
    sum <- c(NULL)
  
    for(i in 1:length(steps)){
      if( i == 1){
        sum <- c(sum, k + steps[i])
      }
      sum <- c(sum, sum[i-1] + steps[i])
    }
  
    plot(sum, ylab = "Total gained", xlim = c(0,1000), ylim=c(0,limit) )
    
  }

  #terminar
	
	if (stake == 0) 
	   return(1) 
	else 
	  return(0)
	}   

k <- 20 
limit <-  60  
p <- 1/2  # Probabilidad de ganar cada intento
trials <- 100 # Numero de intentos del juego

#simular 1000
simlist <- replicate(trials, gamble(k, limit, p, graficar = TRUE)) # LLevamos a cabo varios intentos del juego y guardamos los resultados en un vector
cat("Probabilidad de ir a la ruina: ")
mean(simlist) # Estimate of probability that gambler is ruined
# For p = 0.5, exact probability is (n-k)/n

x<- 20  # Capital inicial 
b<- 60  # Monto total
p<- 0.5 # Probabilidad de victoria de cada juego
trials<- 1000  # Numero de veces que se llevara a cabo la simulacion de ruina del                       jugador
simlist<- replicate(trials,gamble(x,b,p, graficar = FALSE)) # replicamos los juegos muchas veces
cat("Probabilidad de ir a la ruina: ")
mean(simlist)

```
```{r}
# pizza.R
# Example 1.25
# Simulation of Bob's pizza probability

trials <- 10000
simlist <- numeric(trials)
toppings <- c("pepper","pepperoni","pineapple","prawns","proscuitto")

for (i in 1:trials) {
  pineapple <- 0
  pepperoni <- 0
  while (pineapple == 0) {
     pick <- sample(toppings,1)
     if (pick == "pepperoni") pepperoni <- pepperoni + 1
     if (pick == "pineapple") pineapple <- 1
  }
  
  simlist[i] <- pepperoni
}

mean(simlist)


```

```{r}
trials <- 100000
simlist <- numeric(trials)

for (i in 1:trials) {
  expense <- rexp(1,1/500)
  payout <- max(0, expense-100)
  simlist[i] <- payout
}

mean(simlist)
sd(simlist)



```
## Ejercicios 1.32 - 1.37

**1.32 Simulate flipping three fair coins and counting the number of heads X.
a) Use your simulation to estimate P(X=1) and E(X)
b) Modify the above to allow for a biased (cargada o truqueada) where P(Heads) = 3/4
**

```{r}

FlippingCoin = function(p_head, n_throws){
  flip_list <- c(NULL)
  
  for (i in 1:n_throws) {
    flip <- sample(c("H","T"), 1, prob = c(p_head, 1-p_head)) #Head : H, Tail: T
    flip_list <- c(flip_list, flip)
  }
  
  n_heads = 0
  for (i in 1:3) {
    if (flip_list[i] == "H") {
      n_heads <- n_heads + 1
    }
  }
  
  return (n_heads)
}

FlippingCoin_first_head = function(p_head, n_throws){
  flip_list <- c(NULL)
  
  for (i in 1:n_throws) {
    flip <- sample(c("H","T"), 1, prob = c(p_head, 1-p_head)) #Head : H, Tail: T
    flip_list <- c(flip_list, flip)
  }
  
  if(flip_list[1] == "H"){
    return(1)
  }else {
    return(0)
  }
}

#parámetros
p_head = 1/2
n_throws = 3
replications <- 1000

simlist_1 <- replicate(replications, FlippingCoin(p_head, n_throws))
cat("Media de caras en 3 tiros: ", mean(simlist_1))


#simulaciones para calcular la probablidad de que la primer moneda sea cara
simlist_2 <- replicate(replications, FlippingCoin_first_head(p_head, n_throws))
cat("\nMedia de que el primer lanzamieno sea cara :", mean(simlist_2))

```

**1.33 Cards are drawn from a standard deck, with replacement, until an ace appears. Simulate the mean and variance of the number of cards required. ** 

Un mazo tiene 48 cartas
4 palos de 12 cartas
la carta 1 es el as

```{r}
deck_cards = function (looking_for) {
  deck <- rep(c(1:12),4)
  cards <- c(NULL)
  n <- 0
  
  while (n <= 48 ) {
    chosen_card <- sample(deck, 1)
    
    n <- n + 1
    
    if(chosen_card == 1){
      break
    }
    
    #Quitar la carta que salio del maso
    deck <- deck[-which(deck == chosen_card)[1]]
    
  }
  
  return(n)
}

replications <- 1000
simlist <- replicate(replications, deck_cards(1))
cat("Movimientos promedio para encontrar el as: ",mean(simlist),"\n")
cat("Varianza :", var(simlist))

```
** 1.34 The time until a bus arrives has an exponential distribution with mean 30 minutes
a) Use the command rexp() to simulate the probability that the bus arrives in the first 20 minutes.
b) Use the command pexp() to compare with the exact probability
**
```{r}
n <- 10000
arrival_time <- rexp(n, rate = 1/30) #mean = 1/rate 

first_minutes <- arrival_time[ arrival_time <= 20]

probability <- length(first_minutes)/n

confirmed_prob <- pexp(20, rate = 1/30)
cat("Probabilidad de acuerdo a la poblacion", probability, "\n")
cat("Función de distribucion ", confirmed_prob)

```
** 1.35 See the script file gamblersruin.R. A gambler starts with a $60 initial stake.
a) The gambler wins, and loses each round with probabilty p = 50. Simulate the probability the gambler wins $100 before he loses everything.
b) The gambler wins each round with probability p = 0.51. Simulate the probability the gambler wins $100 before he loses everything.
**
```{r}
k <- 60 
limit <-  100  
p <- 0.50  # Probabilidad de ganar cada intento
trials <- 1000 # Numero de intentos del juego

#simular 1000
simlist <- replicate(trials, gamble(k, limit, p, graficar = FALSE))
cat("Probabilidad de que gane $100 con p = 0.50\n")
print(1-mean(simlist))

p <- 0.51
trials <- 100
simlist <- replicate(trials, gamble(k, limit, p, graficar = TRUE))
cat("Probabilidad de que gane $100 con p = 0.51\n")
print(1-mean(simlist))
```
** 1.36 See Example 1.2 and the script  file ReedFrost.R. Observe the effect on the course of the disease by changing the initial values for the number of people susceptible and infected. How does increasing the number of infected people affect the duration of the disease **

```{r}
Z<-SIR(160,10,0.004)

X<- Z[[1]]
Y<- Z[[2]]
W<- Z[[3]]
X<- unlist(X)
Y<- unlist(Y)
W<- unlist(W)
#plot(X,cex=2)
#plot(Y)
plot(X, xlab="time (t).", ylab= "Susceptible number", 
     cex=1, type="o", xlim=c(0,30), ylim=c(0,100) , lty="solid",xaxp=c(0,30,10),yaxp=c(0,100,100))

plot(Y, xlab="time (t).", ylab= "Total Infected number", 
     cex=1, type="o", xlim=c(0,30), ylim=c(0,100) , lty="solid",xaxp=c(0,30,10),yaxp=c(0,100,100))



plot(W, xlab="time (t).", ylab= "Infected number", 
     cex=1, type="o", xlim=c(0,30), ylim=c(0,100) , lty="solid",xaxp=c(0,30,10),yaxp=c(0,100,100))
```
```{r}
Z<-SIR(160,30,0.004)

X<- Z[[1]]
Y<- Z[[2]]
W<- Z[[3]]
X<- unlist(X)
Y<- unlist(Y)
W<- unlist(W)
#plot(X,cex=2)
#plot(Y)
plot(X, xlab="time (t).", ylab= "Susceptible number", 
     cex=1, type="o", xlim=c(0,30), ylim=c(0,100) , lty="solid",xaxp=c(0,30,10),yaxp=c(0,100,100))

plot(Y, xlab="time (t).", ylab= "Total Infected number", 
     cex=1, type="o", xlim=c(0,30), ylim=c(0,100) , lty="solid",xaxp=c(0,30,10),yaxp=c(0,100,100))



plot(W, xlab="time (t).", ylab= "Infected number", 
     cex=1, type="o", xlim=c(0,30), ylim=c(0,100) , lty="solid",xaxp=c(0,30,10),yaxp=c(0,100,100))
```
A: incrementar la cantidad de personas infectadas, disminuye el tiempo que toma infectar a todas las personas susceptibles

** 1.37 Simulate the results of Exercise 1.28. Estimate the mean and variance of the number of accidents per day.

Excersie 1.28 
On any day, the number of accidents on the highway has a Poisson distribution with parameter A. The parameter A varies from day to day and is itself a random variable. Find the mean and Variance of the number accidents per day when A is uniformly distributed on (0,3)
**

```{r}

accidents <- function(){
  day <- runif(1, min = 0, max = 3)
  accidents <- rpois(1, day)
  
  return(accidents)
}

replications <- 10000
simlist <- replicate(replications, accidents())
cat("Promedio de accidentes por día ", mean(simlist), "\n")
cat("Varianza de accidentes por día ", var(simlist), "\n")


```

