---
title: "Práctica 1"
author: "Diego Gutiérrez Gonz"
output:
  html_document:
    df_print: paged
---


1.- Create one vector, containing the sequence of numbers from -10 to 27. Print on the screen the seventh element.

```{r}

x1 <- c(seq(-10, 27, by=1))
print(x1)
cat("\nSeventh element in the sequence ", x[7])

```

2.- Create one vector, containing the sequence of numbers from 0 to 40. Then, create the vector {3(5^n) −1 | n=0,..40 }.

```{r}

x2 <- seq(0, 40, by=1)
x2
cat("\n")
x2_transformed <- 3*(5**x2)-1
x2_transformed

```
3.- Consider the vector in the previous exercise.
You are given:

    h - the highest volume allowed for any song

    i - the initial volume before the first song

    A - a list of allowed volume changes for the following songs
    
    singer(h, i, A)

- The singer can either increase/decrease the volume of sound system for the next song by the allowed volume change A[j] for jth song from the volume of the j-1th song. 

- The singer's objective is to maximize the volume of the last song

- The volume cannot be a negative number
Objective: write a function that finds the maximum volume that can be attained, or return -1 if there is no possibility of changing volume due to the given constrains. 

- Examples:

singer(10, 1, [4,4,4,4]) 
    1st song: can go up 4 from 1 -> volume 5; can't go down 4 from 1 (1-4 < 0)
    2nd song: can go up 4 from 5 -> volume 9; can go down 4 from 5 -> volume 1
    3rd song: volume 9 can't go up but can go down -> volume 5; volume 1 can't go down but can      go up -> volume 5
    4th song: volume 5 can go up -> 9; volume 5 can go down -> 1
    Return 9
    
singer(4, 1, [4,4,4]) 
    1st song: can't go up 4 from 1 (1+4>4); can't go down 4 from 1 (1-4 < 0)
    Return -1, can't change volume
    
singer(3, 1, [1,2,3]) 
    1st song: can go up 1 from 1 -> volume 2; can go down 1 from 1 -> volume 0
    2nd song: can´t go up 2 from 2 -> volume 2 (2+2 > 3); can go down 2 from 2 -> volume 0;
    3rd song: can go up 3 from 0; can´t go down 3 from 0 (0-3 < 0)
    Return 3
    
```{r}

checkVolume <- function(value, index, operations, max, A){
  result <- 0
  
  if(index <= length(A)){
    
    if(value + A[index] <= max){
      result <- value + A[index]
      operations <- c(operations, result)
      #print(operations)
      checkVolume(result, index + 1, operations, max, A)
      
    }else{
      
      result <- value - A[index]
      
      if(result >= 0){
        operations <- c(operations, result)
        #print(operations)
        checkVolume(result, index + 1, operations, max, A)
        
      }else if(result < 0){
        #Not able to Maximize the volume
        operations <- c(operations, result, -1)
        #print(operations)
        return(operations)
      }
    }
  }else{
    return(operations) #return the last item of the vector
  }
}

singer <- function(h, i, A){
  max <- h
  start <- i
  operations <- c(start)
  
  operations <- checkVolume(start, 1, operations, max, A)
  #show the procedure and result
  result <- operations[length(operations)]
  
  if(result >= 0){
    print(operations)
    cat("The maximum volume for the last song is ", operations[length(operations)])  
  }else{
    print(operations)
    print("There is no possibility of changing volume due to the given constrains")
  }
  
}


singer(10, 1, c(4,4,4,4))
singer(4, 1, c(4,4,4)) 
singer(3, 1, c(1,2,3))

```

